DRAFT \\ From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics

### 2016-05-18 2015CompleteDerivation/completeDerivation.tex
Added justification for symplectic manifold

\begin{justification}
	TODO: we can search for omega looking from constraints. Must be linear. Must be skew-symmetric (applied to the same vector twice must be zero). Must be invariant by coord transformation.
\end{justification}

>>>>

\begin{justification}
	We claim $\mathcal{S}$ is a differential manifold. A composite state $\mathcal{c}$ is a distribution $\rho_\mathcal{s} : \mathcal{S} \rightarrow \mathbbm{R}$. $\rho_\mathcal{c}$ is defined on any chart of $\mathcal{S}$. Given two charts, for any $\rho_\mathcal{c}(q)$ there is a corresponding $\rho_\mathcal{c}(q')=\rho_\mathcal{c}(q^i) | d q' / d q |$. The Jacobian $| d q' / d q |$ exists and is non-zero. The map between any two charts is differentiable. $\mathcal{S}$ is a differentiable manifold.

	We claim the simplest state space $\mathcal{S}$ that allows state-variable-invariant densities is the symplectic manifold $(T^*\mathcal{Q}, \omega)$ where $T^*\mathcal{Q}$ is the cotangent bundle of a one dimensional differential manifold $\mathcal{Q}$ and $\omega$ is the canonical two-form. The description of the simplest physical object on which we can  state-variable-invariant must be given by at least one state variable $q$. Let $\mathcal{Q}$ be the manifold charted by $q$. $\mathcal{Q} \subseteq \mathcal{S}$. $\mathcal{Q}$ is differentiable. Let's assume $q$ is enough to define the unit system for the description of the physical object. Then the physical object is represented by a set of geometrical objects in $\mathcal{Q}$. The physical object is infinitesimal, therefore is represented by a local geometrical object. The simplest geometrical object in $\mathcal{Q}$ is a point, charted by $q$. A density over points is not invariant: $\rho(q')_\mathcal{c}= \rho(q)_\mathcal{c} dq/dq'$. Next we consider local geometrical objects charted by 2 variables. Densities over vectors $v(q) e_q \in T\mathcal{Q}$ are not invariant: $\rho_\mathcal{c}(q', v')= \rho(q, v)_\mathcal{c} (dq/dq')^2$. Densities over covectors $k(q) dq \in T^*\mathcal{Q}$ are invariant: $\rho_\mathcal{c}(q', k')= \rho_\mathcal{c}(q, k) (dq/dq') (dq'/dq) = \rho_\mathcal{c}(q, k)$. Covectors are the simplest geometrical object to allow unit independent densities. The state space $\mathcal{S}$ for the simplest object that allows state-variable-independent densities is $T^*\mathcal{Q}$ of a one dimensional differential manifold $\mathcal{Q}$. Express integration in coordinates. $\int_{\mathcal{S}} \rho_\mathcal{c} d\mu \propto \int_{\mathcal{S}} \rho_\mathcal{c}(q, k) dq \wedge dk$. $d\mu = \hbar dq \wedge dk = dq \wedge dp = \omega$ where $\hbar$ is a constant and $\omega$ is the canonical two form. $\omega$ is invariant under state variable change. $\omega$ is a symplectic metric for $\mathcal{S}=T*\mathcal{Q}$. $\mathcal{S} \cong(T^*\mathcal{Q}, \omega)$ as a symplectic manifold.

	We claim the state space $\mathcal{S}$ for the particles of a homogeneous classical material is a symplectic manifold $(T^*\mathcal{Q}, \omega)$ where $T^*\mathcal{Q}$ is the cotangent bundle of a one dimensional differential manifold $\mathcal{Q}$ and $\omega$ is the canonical two-form. Let $q^i$ be a set of n continuous independent state-variable that define the units to describe a state in $U \subseteq \mathcal{S}$. Let $\mathcal{Q}$ be the manifold charted by $q^i$. Locally $\mathcal{Q} \cong \prod \mathcal{Q}^i \cong \mathbbm{R}^n$. Changing units of one state variable must not change the units of the other as they are independent. Each degree of freedom must define state-variable-distribution independently. For each $\mathcal{Q}^i$ we need a covector $k_i(q) dq^i \in T^*\mathcal{Q}^i$. Locally $\mathcal{S} \cong \prod T^*\mathcal{Q}^i \cong T^* \prod \mathcal{Q}^i \cong T^* \mathcal{Q}$. Integration must also be defined on an independent d.o.f. There must exist a non degenerate two-form $\omega$ such that $\int_{U \subset \mathcal{S}} \rho_\mathcal{c} \omega$ where $U$ is any two dimensional surface in $\mathcal{S}$. $\omega$ has to be form invariant under state variable change. The canonical two-form is the only such form. $\omega = \sum dq^i \wedge dp_i$. $\mathcal{S} \cong (T^*\mathcal{Q}, \omega)$ as a symplectic manifold.
\end{justification}
